---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# tellme

## Background

As I do exploratory data analysis, I often find myself wondering about a variety of stats that both the `summary()` and the `glimpse()` functions are unable to provide. For instance, I like to know the mean, median, standared deviation, 5th percentile, 10th percentile, etc. While the aforementioned functions do a good job of providing *some* insight, I felt the need to develop a more powerful way of getting the summaries I wanted.

Hence, the tellme package was born.

<!-- badges: start -->
<!-- badges: end -->

The goal of tellme is to provide a much better summary of the different numeric and non-numeric columns of data. Often, I find that the `summary()` or the `dplyr::glimpse()` functions are unable to provide a comprehensive summary of the underlying data.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nikdata/tellme")
```
## Example 1: Summarizing Numerical Data

```{r numerical_data}
library(tellme)

tellme::the_numbers(iris)
```

## Example 2: Summarizing Non-Numerical Data

```{r non_numerical_data}
library(tellme)

tellme::the_characters(iris)
```
